Methodology for Assessing the State of the Practice for Domain X

### 2020-10-01 StateOfPractice/Methodology/Methodology.tex
updated and commented on sections 2, 5, 6 of Methodology based on meeting discussion

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What information is captured by current software project
  artifacts? \pmi{keep} \wss{This question probably isn't part of the state of
    the practice exercise, but part of Olu's PhD research.}
\item What are attitudes of research software developers and engineer toward:
\begin{enumerate}
\item sustainability?
\item productivity?
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

@@

\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather empirical measures found in Section \ref{SecEmpiricalMeasures}.
	\item \ad{``Ideally have the latest release or source code commit within the last 5 years.'' How about this one? Do we care about the ``vintage'' software?}\pmi{I tested some software that has not been updated in about 8 years, as this software was mentioned in multiple places and looked professional. That being said, age should be noted as something that is considered along with other qualities. "Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use."}
\end{enumerate}

@@

\begin{enumerate}
	\item Organization - The software and any related documentation should appear to be easy to gather and understand.
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\ad{What if installation or usage procedures are unavailable? I think we're measuring that if the software have installation instructions and user manuals,
	so perhaps they should be kept even if these docs are missing.}
    \pmi{How are we installing the software if such documents and procedures are missing? Should we expect users to be able to install? I did not encounter a situation where even basic installation steps were missing.}
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
	\item \ad{What if there are still more candidates than we need? Should we also filter out the ``older'' or ``less popular'' ones if needed? }\pmi{Good question. Let's discuss during meeting.}
\end{enumerate}

>>>>

\begin{enumerate}
\item What artifacts do current software projects produce?  \pmi{keep}
\item What are the attitudes and actions of research software developers and toward:
\begin{enumerate}
\item sustainability?
\item usability?
\item modifiability? \pmi{think about and possibly remove this one}
\end{enumerate} \pmi{keep} \wss{What are we hoping to learn from this question?
  This might be a question for Olu, since she currently has the same research question.}
\item For a given domain of research software, what current projects provide the
  best examples of high quality software and documentation? \wss{Reworded
    version of one of Olu's research questions.}
\end{enumerate}

@@

\begin{enumerate}
	\item Major function(s) must fall within the identified domain.
	\item Must have viewable source code.
	\item Ideally have a git repository or ability to gather empirical measures found in Section \ref{SecEmpiricalMeasures}.
	\item Status - The software cannot be marked as incomplete or in an initial development phase.
\end{enumerate}

@@

\begin{enumerate}
	\item Restrict scope (functionality?)\pmi{elaborate on this}
	\item Can we install? \pmi{elaborate on this, copy from point below?}
	\item Available documentation - The purpose of the software and the installation and usage procedures should appear to be moderately clear or easy to find.
	\ad{What if installation or usage procedures are unavailable? I think we're measuring that if the software have installation instructions and user manuals,
	so perhaps they should be kept even if these docs are missing.}
    \pmi{How are we installing the software if such documents and procedures are missing? Should we expect users to be able to install? I did not encounter a situation where even basic installation steps were missing.}
	\item \ad{What if there are still more candidates than we need? Should we also filter out the ``older'' or ``less popular'' ones if needed? }\pmi{Good question. Let's discuss during meeting.}\pmi{meeting: add point about dropping off oldest ones, look at the point below copied from previous section}
	\item \ad{``Ideally have the latest release or source code commit within the last 5 years.'' How about this one? Do we care about the ``vintage'' software?}\pmi{I tested some software that has not been updated in about 8 years, as this software was mentioned in multiple places and looked professional. That being said, age should be noted as something that is considered along with other qualities. "Ideally the latest release or source code commit should be relatively recent, such as within the last 5 years, unless the candidate software appears to be well recommended and currently in use."}

\end{enumerate}
